An excess of positive results: Comparing the standard Psychology literature with Registered Reports

### 2020-01-13 appendix/appendix.Rmd
fixed typos

##### Excluding Registered Replication Reports (RRRs):
The decision to exclude all RRRs was made during the main data collection (coding round 1), i.e. after piloting and after the study had been preregistered. 
MS and AS both noted that RRRs were particularly difficult to code because no clear hypothesis and/or no clear conclusions could be identified. 
This lead us to look up the editorial information for the RRR format, which clearly states that RRRs are not supposed to test hypotheses:  
'The conclusion of a Registered Replication Report should avoid categorizing each result as a success or failure to replicate. Instead, it should focus on the cumulative estimate of the effect size' (retrieved from https://www.psychologicalscience.org/publications/replication). 
Therefore we decided to categorically exclude all RRRs, regardless of whether or not we were able to code them.

@@

### 3.2.2 Replication status
Since the difference between replication studies and original studies was not the main focus of our paper, and because definitions of (e.g.) direct versus conceptual replications can be difficult to apply, we originally aimed for a 'lightweight' coding criterion and coded two binary variables: 'contains replication' and 'contains original work'. 
Both of these pertained to a full paper and were not restricted to the first hypothesis, meaning that a paper could be coded as 'contains a replication' even if the coded hypothesis was clearly novel. 
A paper could be coded as containing only replication research (i.e., 'contains replication' = 1, 'contains original work' = 0), only original work (i.e., 'contains replication' = 0, 'contains original work' = 1), or both (i.e., 'contains replication' = 1, 'contains original work' = 1), but not neither. 
However, we did not define any precise criteria for what would vs would not constitute a replication, which lead to coding disagreements between MS and AS for a relatively large number of papers (MS had used a relatively lenient, AS a quite strict definition of 'contains replication'). 
We therefore decided (after MS had completed his BEP thesis) to completely revise the way in which replication status was coded.

The main reason why we coded replication status in the first place was the idea that direct replication studies may sometimes or often be motivated by the authors' scepticisim of the original result, and that such direct replication studies may be overrepresented in the Registered Reports population compared to the standard literature. 
Therefore, we chose to focus on whether the authors' goal appeared to be to test if a previously published result holds up by conducting a close replication of the respective original study. 
We would thus ignore replications that had the goal to test if a hypothesis or method holds in a new context or population (i.e., that did not have the goal to challenge or verify the results in the original context or population) and 'internal' replications (i.e., replications of studies published in the same paper).

>>>>

##### Excluding Registered Replication Reports (RRRs):
The decision to exclude all RRRs was made during the main data collection (coding round 1), i.e. after piloting and after the study had been preregistered. 
MS and AS both noted that RRRs were particularly difficult to code because no clear hypothesis and/or no clear conclusions could be identified. 
This led us to look up the editorial information for the RRR format, which clearly states that RRRs are not supposed to test hypotheses:  
'The conclusion of a Registered Replication Report should avoid categorizing each result as a success or failure to replicate. Instead, it should focus on the cumulative estimate of the effect size' (retrieved from https://www.psychologicalscience.org/publications/replication). 
Therefore we decided to categorically exclude all RRRs, regardless of whether or not we were able to code them.

@@

### 3.2.2 Replication status
Since the difference between replication studies and original studies was not the main focus of our paper, and because definitions of (e.g.) direct versus conceptual replications can be difficult to apply, we originally aimed for a 'lightweight' coding criterion and coded two binary variables: 'contains replication' and 'contains original work'. 
Both of these pertained to a full paper and were not restricted to the first hypothesis, meaning that a paper could be coded as 'contains a replication' even if the coded hypothesis was clearly novel. 
A paper could be coded as containing only replication research (i.e., 'contains replication' = 1, 'contains original work' = 0), only original work (i.e., 'contains replication' = 0, 'contains original work' = 1), or both (i.e., 'contains replication' = 1, 'contains original work' = 1), but not neither. 
However, we did not define any precise criteria for what would vs would not constitute a replication, which led to coding disagreements between MS and AS for a relatively large number of papers (MS had used a relatively lenient, AS a quite strict definition of 'contains replication'). 
We therefore decided (after MS had completed his BEP thesis) to completely revise the way in which replication status was coded.

The main reason why we coded replication status in the first place was the idea that direct replication studies may sometimes or often be motivated by the authors' scepticism of the original result, and that such direct replication studies may be overrepresented in the Registered Reports population compared to the standard literature. 
Therefore, we chose to focus on whether the authors' goal appeared to be to test if a previously published result holds up by conducting a close replication of the respective original study. 
We would thus ignore replications that had the goal to test if a hypothesis or method holds in a new context or population (i.e., that did not have the goal to challenge or verify the results in the original context or population) and 'internal' replications (i.e., replications of studies published in the same paper).

### 2020-01-13 preprint/manuscript.Rmd
fixed typos

### Replication status
We also wanted to code if a study was a replication of a previously published one: 
We expected a much larger proportion of Registered Reports to be direct replications, many of which may have been motivated by scepticism of the original study. 
A lower positive result rate in Registered Reports could then be an effect of failed replications rather than an effect of safeguards against QRPs and publication bias. 
After an initial coding attempt with ill-defined coding criteria lead to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered): 
We searched the full texts of all papers for the string "replic$^\ast$" [cf. @Makel2012; @Kohler2019; @Mueller-Langer2019; @Pridemore2018], and for those that did contain it determined whether the first hypothesis was a close or direct replication of previously published work. 
Conceptual replications and internal replications were not counted as replications in this narrow sense: 
The reason to code replication status in the first place was the idea that direct replications of previous work may be motivated by replicators' scepticism in the hypothesis and thus have a low prior probability, whereas conceptual replications are usually considered as building on previous work rather than verifying it. 
AS coded all papers, DL double-coded `r rep.RR.coded.DL` Registered Reports ($`r printnum(rep.RR.coded.DL/sum(included$is_RR)*100)` \%$) and `r rep.SR.coded.DL` standard reports ($`r printnum(rep.RR.coded.DL/sum(included$is_RR==0)*100)` \%$). 
There were `r rep.disagreements` disagreements (Cohen's kappa = `r printp(kappa.rep)`), all were resolved by discussion.

@@

## Limitations
We compared hypotheses tested in Registered Reports with hypotheses tested in standard reports. 
Because neither hypotheses, authors, nor editors are randomly assigned to each publication format we cannot draw firm conclusions about the causes that lead to a difference in the proportion of supported hypotheses. 
Although it seems plausible that selective reporting and QRPs are reduced in Registered Reports, we do not know by how much, nor if this reduction would be of comparable size in a randomised experiment. 
As mentioned above, it is a-priori plausible that the Registered Reports format is used selectively for particularly risky hypotheses. 
This means that the proportion of true hypotheses in Registered Reports does not necessarily generalise to the entire population of hypotheses that are tested in psychology. 
It is also important to note that our results do not warrant the conclusion that Registered Reports are effective at reducing all forms of bias. 
Authors self-select to submit Registered Reports, and the format may be particularly popular among those who try to minimise the risk of inflated error rates regardless of the report format they use. 
This would lead to less bias in the Registered Reports literature even if the format's safeguards against certain QRPs were actually ineffective.

>>>>

### Replication status
We also wanted to code if a study was a replication of a previously published one: 
We expected a much larger proportion of Registered Reports to be direct replications, many of which may have been motivated by scepticism of the original study. 
A lower positive result rate in Registered Reports could then be an effect of failed replications rather than an effect of safeguards against QRPs and publication bias. 
After an initial coding attempt with ill-defined coding criteria led to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered): 
We searched the full texts of all papers for the string "replic$^\ast$" [cf. @Makel2012; @Kohler2019; @Mueller-Langer2019; @Pridemore2018], and for those that did contain it determined whether the first hypothesis was a close or direct replication of previously published work. 
Conceptual replications and internal replications were not counted as replications in this narrow sense: 
The reason to code replication status in the first place was the idea that direct replications of previous work may be motivated by replicators' scepticism in the hypothesis and thus have a low prior probability, whereas conceptual replications are usually considered as building on previous work rather than verifying it. 
AS coded all papers, DL double-coded `r rep.RR.coded.DL` Registered Reports ($`r printnum(rep.RR.coded.DL/sum(included$is_RR)*100)` \%$) and `r rep.SR.coded.DL` standard reports ($`r printnum(rep.RR.coded.DL/sum(included$is_RR==0)*100)` \%$). 
There were `r rep.disagreements` disagreements (Cohen's kappa = `r printp(kappa.rep)`), all were resolved by discussion.

@@

## Limitations
We compared hypotheses tested in Registered Reports with hypotheses tested in standard reports. 
Because neither hypotheses, authors, nor editors were randomly assigned to each publication format we cannot draw firm conclusions about the causes that led to a difference in the proportion of supported hypotheses. 
Although it seems plausible that selective reporting and QRPs are reduced in Registered Reports, we do not know by how much, nor if this reduction would be of comparable size in a randomised experiment. 
As mentioned above, it is a-priori plausible that the Registered Reports format is used selectively for particularly risky hypotheses. 
This means that the proportion of true hypotheses in Registered Reports does not necessarily generalise to the entire population of hypotheses that are tested in psychology. 
It is also important to note that our results do not warrant the conclusion that Registered Reports are effective at reducing all forms of bias. 
Authors self-select to submit Registered Reports, and the format may be particularly popular among those who try to minimise the risk of inflated error rates regardless of the report format they use. 
This would lead to less bias in the Registered Reports literature even if the format's safeguards against certain QRPs were actually ineffective.
